### 2015-06-22 narrative/intro.tex
added some clarifying questions for discussion

>>>>

We are aiming to spread an output across the vertical layers of the storage
hierarchy simultaneously.  When data should migrate to a higher tier, what
happens to the existing version?

Is there a canonical copy that is the originally written version?

Is there annotation about this (I think so) attached to that part of the variable?

At the tape layer, we see having a lossy compressed version just above the tape
layer used as a directory/index and then the ``full'' resolution version on
tape only retrieving once the user accepts the time/quality tradeoff. This is
going to require some serious language to describe. If we have 100s PB of tape
space, we'll need 1s PB of disk even at a 99\% data reduction. That is
non-trivial.

What happens when that data is retrieved from tape? Is a third copy made in an
appropriately sized/quality level version for the tier it is requested to be
pulled to? What if it is just the index version? Or the on tape version? Does
it have a TTL because of the pain retrieving it from tape?

Do we specify a target tier or just allow the system to place it in a place
that makes sense? Given the potential space limitations, I think this is pretty
critical because it could cause evictions or other insufficient space actions
that are unintended. I can see us specifying that when you ask for data to be
pulled at a particular quality level to a particular performance tier that it
is a best effort with the use specifying if compromise or just failure is the
result if the request cannot be fulfilled.  Making this interaction make sense
is going to require some reasonable thought and testing. We'll probably need to
run it past apps people to get their feedback too as I don't think we are able
to give a solid answer without some broad input.

How does the migration to ``data lakes''/``campaign storage'' work? How does the
migration to tape ultimately happen? I think we need to incorporate some
explicit staging commands to move data both up and down the stack along with
some variability in placement based on data features and current system state.

Given the storage scarcity, particularly for NVM, I think we need to have a
solid story here as part of the proposal. Yes, there are questions that have to
be answered to build this still, but we need to have some pretty solid clarity
where possible. I don't feel like I can explain it well enough at what I
believe to be a proper clarity level at this point.
